\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage[none]{hyphenat}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{float}
\usepackage[nottoc, notlot, notlof]{tocbibind}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\slshape \MakeUppercase{Cassette deck}}
\fancyhead[R]{\slshape Modélisation}
\fancyfoot[C]{\thepage}
%\renewcommand{\headrulewidth}{0pt} %to remove the horizontal line in header
\renewcommand{\footrulewidth}{0pt} %to remove the horizontal line in footer

\parindent 0ex %removes paragraph indentation
%\setlength{\parindent}{4em} %change the width of the indent
%\setlength{\parskip}{1em} %change the amount of spacing between paragraphs
\renewcommand{\baselinestretch}{1.5} %affects line spacing of paragraphs 

\begin{document}

\begin{titlepage}
\begin{center}
\vspace*{1cm}
\Large{\textbf{Génie Logiciel}}\\
\Large{\textbf{Projet de Modélisation et d’Implémentation}}
\vfill
\line(1,0){400}\\[1mm]
\huge{\textbf{“Simulator of a Cassette Deck”}}\\[3mm]
\Large{\textbf{- Partie modélisation -}}\\[1mm]
\line(1,0){400}\\
\vfill
Par Constant Théo et Essafsyfy Abdelkrim\\
%Candidate \#\\
\today
\end{center}
\end{titlepage}

\tableofcontents
\thispagestyle{empty} %removes header and footer from table of contents
\clearpage %table of content on its own page

\setcounter{page}{1} %1st page is after table of contents

\section{Maquette de l'interface graphique}
\subsection{\textit{Launcher}}
\subsection{Application}
\section{Diagrammes UML}
\subsection{Diagramme de cas d'utilisation}
\textbf{Use case name} : Record Music\\
\textbf{Summary} : User records music from external audio input device on cassette.\\
\textbf{Actors} : User (primary), Audio Input Device (secondary)\\
\textbf{Assumptions} : Cassette deck is connected to audio input device. Both devices and their connection are working
correctly.\\
\textbf{Preconditions} : Cassette desk is powered on. Cassette is inserted in cassette holder. Cassette desk is in idle state.\\
\textbf{Basic course of action :}\\
1. User pressesj button.\\
2. System rewinds cassette to the beginning of the magnetic tape and stops.\\
3. System releasesj button.\\
4. User resets counter to 0.\\
5. User selects audio input device, and starts playing audio from this device.\\
6. User presses Û of the cassette deck.\\
7. System engages magnetic head on tape and signals recording status with indicator light.\\
8. System starts recording on the cassette from the selected input device.\\
9. User depresses Û to stop recording.\\
10. System disengages magnetic head from tape and signals idle status with indicator light.\\
\textbf{Postconditions} : Same as preconditions.\\
\textbf{Alternate courses :}\\
9a : System detects that end of tape is reached. System releases Û button to stop recording. Go to step 10.\\
9b : [If auto reverse functionality is present and enabled :] System detects that end of tape is reached. System
disengages magnetic head,
\subsection{Diagramme de classes}
\subsection{Diagramme d'état \textit{(Yakindu)}}
\subsection{Diagramme de séquence}
\subsection{Diagramme d'activité}
\subsection{Diagramme bonus?}

\end{document}